A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-05-23 intro.tex
adding citations

Integrated Assessment Models (IAMs) are tools used to understand the complex
interactions between energy systems, economoic systems, land use, the climate,
and air pollution, among other sectors \TODO{cite some IAMs}. IAMs provide
global projections of systemic change by dividing the world into a number of
representative regions, the definition of which is distinct for each
model. Results from IAMs are integral in a number of international studies,
which notably include projections of climate and economic futures used in
analyses underpinning the Intergovenmental Panel on Climate Change (IPCC)
\TODO{cite} and the United Nations Framework Convention on Climate Unchange
(UNFCCC)'s Paris Agreement \TODO{cite}.

@@

Harmonization has been addressed in previous studies as it is a common practice
in the IAM and climate change communities. For example, \TODO{cite Malte}
describes a harmonization process using scaling routines for the 5 SRES regions
with no sectoral definition. Further, \TODO{cite Joeri} describes the impacts of
choosing various harmonization routines on future trajectories. Importantly, the
choice of harmonization method to date has been determined via expert
solicitation and has generally been applied to all trajectories for a given
class of emissions species.

>>>>

Integrated Assessment Models (IAMs) are tools used to understand the complex
interactions between energy systems, economoic systems, land use, the climate,
and air pollution, among other sectors \cite{van_vuuren_energy_2017,
  kriegler_fossil-fueled_2017, calvin_ssp4:_2017, fujimori_ssp3:_2017,
  fricko_marker_2017}. IAMs provide global projections of systemic change by
dividing the world into a number of representative regions, the definition of
which is distinct for each model. Results from IAMs are integral in a number of
international studies, which notably include projections of climate and economic
futures used in analyses underpinning the Intergovenmental Panel on Climate
Change (IPCC) \TODO{cite} and the United Nations Framework Convention on Climate
Unchange (UNFCCC)'s Paris Agreement \TODO{cite}.

@@

Harmonization has been addressed in previous studies as it is a common practice
in the IAM and climate change communities. For example,
\cite{meinshausen_rcp_2011} describes a harmonization process using scaling
routines for the 5 SRES regions with no sectoral definition. Further,
\cite{rogelj_discrepancies_2011} describes the impacts of choosing various
harmonization routines on future trajectories. Importantly, the choice of
harmonization method to date has been determined via expert solicitation and has
generally been applied to all trajectories for a given class of emissions
species.
